---
title: "Simple document"
output: github_document
 
    
---
```{r,echo=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(readr)
library(ggplot2)
library(p8105.datasets)
library(knitr)
```
 
```{r}
```
 
 
##Problem2
#introduce the dataset
```{r}
library("p8105.datasets")
acc=read_csv("C:/Users/10145/Desktop/p8105_hw2_zx2425(1)/p8105_hw3_zx2425/p8105_hw3_zx2425/accel_data.csv")
acc = acc %>% 
  janitor::clean_names()
```
The demensions of the raw dataset is ```r ncol(acc)``` * ```r nrow(acc)```. It contains the
each minute of activity by days and its costs orginized by wide format.

#clean the dataset
```{r}
acc = acc %>%   
  mutate(weedd = case_when(
    day == "Monday" | day=="Tuesday" | day=="Wednesday" | day == "Thursday"| day == "Friday" ~ "weekday",
    day == "Saturday"|day=="Sunday" ~ "weekend" ,
    TRUE     ~ "" ))
acc = acc %>% 
      mutate(
    sum=rowSums(.[4:1443])
  )
acc=acc %>% 
  pivot_longer(activity_1:activity_1440,names_to="act",values_to="cc") 
acc=acc %>% 
separate(act, into = c("activity_name", "minute")) %>%
  mutate(
    minute=as.numeric(minute)
  ) %>% 
select(-activity_name)
acc
 
```
The demensions of the raw dataset is ```r ncol(acc)``` * ```r nrow(acc)```. It has been translated to long format dataframe which means the activity variables are represented by the time that the action is issued and its costs. Also, there is a weedd variable represent the type of one day (weekend or not). Furthermore, we sum of one day's activity that showed in the sum variable.

```{r}
acc_sum <- unique(data.frame('day' = acc$day_id, 
                      'counts'=acc$sum))
ggplot(acc_sum, aes(x = day, y = counts)) + 
  geom_point()  
```
This part calculate the total counts for each day, and draw a plot to find if there are any trends for each day's activity. The results show that there are not apparent trend. However, during the 10~30 days, there are more regular activities done than at the begining and in the end of those days.
 
#arrange the order and make a plot
```{r}
acc_ar=acc %>% 
  arrange(day_id)
acc_ar
ggplot(acc, aes(x = minute, y = cc , color=day)) + 
  geom_point()  
  
```
It we focus on the distribution of daily points and ignore the difference among weekdays, it shows that athletes are more active during at time of a day and the ending of a day. If compared different days during the week, we can see most of the outline of the figure is composed by green  and red points, which possibly means that people are more active during weekend. We can conclude that for the patients, they keep an eye on their daily sport. And individuals always do more excercise at the morning, noon and evening of a day. They are more likely to get high level of activity during weekend.

##problem3
#introduce data
```{r}
library(p8105.datasets)
data("ny_noaa")
nynoaadat=ny_noaa
```
```{r}
nynoaadat = separate(nynoaadat,date, into= c("year","month",'day'),sep= "-")

nynoaadat=mutate(
  nynoaadat, year=as.numeric(year),month=as.numeric(month),day=as.numeric(day),tmax=as.numeric(tmax),tmin=as.numeric(tmin))

nynoaadat=nynoaadat %>% 
  mutate(
    snow=snow*10,
    snwd=snwd*10
  )
nyno_fre=as.data.frame(table(nynoaadat$snow))

nynoaadat %>% 
  filter(month==1 | month== 7) %>% 
  drop_na(tmax) %>% 
  group_by(month,id,year) %>% 
  summarize(
      average_tmax=mean(tmax)
    ) %>% 
  ggplot(aes(x=year,y=average_tmax,color=month))+geom_point()+
  facet_grid(.~month)
  
```


```{r}
nynoaadat %>% 
  mutate(
    tmax_fahr = tmax * (9 / 5) + 32,
    tmin_fahr = tmin * (9 / 5) + 32) %>% 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE)
ggplot(nynoaadat, aes(x = tmax, y = tmin)) + 
  geom_hex()
```

```{r}
snow100_filter=nynoaadat %>% 
  mutate(
    year=as.numeric(year),
    year1=factor(year)
  )
snow100_filter=filter(snow100_filter, snow>0 & snow<1000, .keep_all=TRUE)


ggplot(snow100_filter, aes(x = snow, fill = year1)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")
