---
title: "p8105_hw3_zx2425"
output: github_document
 
    
---
Dowloading packages
```{r,echo=FALSE, message=FALSE}
library(tidyverse)
library(readxl)
library(readr)
library(ggplot2)
library(p8105.datasets)
library(knitr)
library(patchwork)
```
 
### Problem 0

This solution focuses on a reproducible report containing code and text necessary for Problems 1-3, and is organized as an R Project. This was not prepared as a GitHub repo; examples for repository structure and git commits should be familiar from other elements of the course.

Throughout, we use appropriate text to describe our code and results, and use clear styling to ensure code is readable. 

### Problem 1
```{r}
data("instacart")

instacart = 
  instacart %>% 
  as_tibble(instacart)
instacart
```
#### Answer questions about the data

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns, with each row resprenting a single product from an instacart order. Variables include identifiers for user, order, and product; the order in which each product was added to the cart. There are several order-level variables, describing the day and time of the order, and number of days since prior order. Then there are several item-specific variables, describing the product name (e.g. Yogurt, Avocado), department (e.g. dairy and eggs, produce), and aisle (e.g. yogurt, fresh fruits), and whether the item has been ordered by this user in the past. In total, there are `r instacart %>% select(product_id) %>% distinct %>% count` products found in `r instacart %>% select(user_id, order_id) %>% distinct %>% count` orders from `r instacart %>% select(user_id) %>% distinct %>% count` distinct users.

Below is a table summarizing the number of items ordered from aisle. In total, there are 134 aisles, with fresh vegetables and fresh fruits holding the most items ordered by far. 
 
```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```

Next is a plot that shows the number of items ordered in each aisle. Here, aisles are ordered by ascending number of items.

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(aisle = fct_reorder(aisle, n)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() + 
  labs(title = "Number of items ordered in each aisle") +
  theme(axis.text.x = element_text(angle = 60, hjust = 1))

```

Our next table shows the three most popular items in aisles `baking ingredients`, `dog food care`, and `packaged vegetables fruits`, and includes the number of times each item is ordered in your table.

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>%
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4) %>% 
  arrange(desc(n)) %>%
  knitr::kable()
```

Finally is a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week. This table has been formatted in an untidy manner for human readers. Pink Lady Apples are generally purchased slightly earlier in the day than Coffee Ice Cream, with the exception of day 5.

```{r}
instacart %>%
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  summarize(mean_hour = mean(order_hour_of_day)) %>%
  spread(key = order_dow, value = mean_hour) %>%
  knitr::kable(digits = 2)
```

###problem2
##introduce the dataset
```{r}
library("p8105.datasets")
acc=read_csv("C:/Users/10145/Desktop/p8105_hw2_zx2425(1)/p8105_hw3_zx2425/p8105_hw3_zx2425/accel_data.csv")
acc = acc %>% 
  janitor::clean_names()
acc
```
The demensions of the raw dataset is ```r ncol(acc)``` * ```r nrow(acc)```. It contains the
each minute of activity by days and its costs orginized by wide format.

#clean the dataset
```{r}
acc = acc %>%   
  mutate(weedd = case_when(
    day == "Monday" | day=="Tuesday" | day=="Wednesday" | day == "Thursday"| day == "Friday" ~ "weekday",
    day == "Saturday"|day=="Sunday" ~ "weekend" ,
    TRUE     ~ "" ))
acc = acc %>% 
      mutate(
    sum=rowSums(.[4:1443])
  )
acc=acc %>% 
  pivot_longer(activity_1:activity_1440,names_to="act",values_to="cc") 
acc=acc %>% 
separate(act, into = c("activity_name", "minute")) %>%
  mutate(
    minute=as.numeric(minute)
  ) %>% 
select(-activity_name)
acc
 
```
### Answering the question resulting dataset
The dimension of the resulting data set is ```r ncol(acc)``` * ```r nrow(acc)```. It has been translated to long format data frame which means the activity variables are represented by the time that the action is issued and its costs. Also, there is a 'weedd' variable represent the type of one day (weekend or not). Furthermore, we sum of one day's activity that showed in the sum variable.

##analysis the sum of activity
```{r}
acc_sum <- unique(data.frame('day' = acc$day_id, 
                      'counts'=acc$sum))
ggplot(acc_sum, aes(x = day, y = counts)) + 
  geom_point()  
```

##Answering questions about the trends
This part calculate the total counts for each day, and draw a plot to find if there are any trends for each day's activity. The results show that there are not apparent trend. However, during the 10~30 days, there are more regular activities done than at the begining and in the end of those days.

##arrange the order and make a plot
```{r}
acc_ar=acc %>% 
  arrange(day_id)
acc_ar
ggplot(acc, aes(x = minute, y = cc , color=day)) + 
  geom_point()  
  
```
##Answering questions
It we focus on the distribution of daily points and ignore the difference among weekdays, it shows that athletes are more active during at time of a day and the ending of a day. If compared different days during the week, we can see most of the outline of the figure is composed by green  and red points, which possibly means that people are more active during weekend. We can conclude that for the patients, they keep an eye on their daily sport. And individuals always do more excercise at the morning, noon and evening of a day. They are more likely to get high level of activity during weekend.

###problem3
##introduce data
```{r}
library(p8105.datasets)
data("ny_noaa")
nynoaadat=ny_noaa
```
Firstly, the data frame contains 2595176 objects and 7 variables. Variables include  `r colnames(ny_noaa)`  
So the next step lets organize the data set and have a outlook. 

```{r}
nynoaadat = separate(nynoaadat,date, into= c("year","month",'day'),sep= "-")

nynoaadat=mutate(
  nynoaadat, year=as.numeric(year),month=as.numeric(month),day=as.numeric(day))
```
The resulting dataset is  `r nrow(nynoaadat)` * `r ncol(nynoaadat)`. The new variables are 'year', 'month' and 'day' which is extract by the data variable. The day_id mark a unique day. And the 'prep','snow', 'snwd', are represent the weather condition which have different measurement.  

So next, Let's unified the measurement standard of 'prep', 'snow', 'snwd' and see the frequency of the 'snow'. 

```{r}
nynoaadat=nynoaadat %>% 
  mutate(
   prcp=prcp/10,
   tmax=as.numeric(tmax)/10,
   tmin=as.numeric(tmin)/10
  )
nyno_fre=as.data.frame(table(nynoaadat$snow))
head(nyno_fre)
```
## Answering the questions
First, we divide 10 to each variable of 'prcp','tmin' and 'tmax'. At the same time, after viewing the frequency table of snow we can see the value of 0 is significantly larger than other values, This possibly because the possible of the snow of the city is low. Besides, we are comparing the frequency of no snow with the frequency of snow at a certain level at the city. 

## draw average_tmax plot by years on January and July
```{r}
nynoaadat %>% 
  filter(month==1 | month== 7) %>% 
  drop_na(tmax) %>% 
  group_by(month,id,year) %>% 
  summarize(
      average_tmax=mean(tmax)
    ) %>% 
  ggplot(aes(x=year,y=average_tmax,color=month))+geom_point()+
  facet_grid(.~month)
  
```
According to the plot, we can see the range of tmax in January is [-100,100], and July is [200,310]. The range is pretty different either. On January is about 200, and on July is about 110 which represent the temperature difference in January is higher than in July. Both of them has outliers for exaple there are two extremely cold day on January which should pay more attention to the reason: wheather is the wrong data or not. 

##Draw tmin_tmax and snow plots
```{r}
tmx_tmin=
  ggplot(nynoaadat, aes(x = tmax, y = tmin)) + 
  geom_hex()
tmx_tmin
```

Finally let's analysis the snow weather.
```{r}
snow100_filter=nynoaadat %>% 
  mutate(
    year=as.numeric(year),
    year1=factor(year)
  )
snow100_filter=filter(snow100_filter, snow>0 & snow<100, .keep_all=TRUE)


dst1=ggplot(snow100_filter, aes(x = snow, fill = year1)) + 
  geom_density(alpha = .4, adjust = .5, color = "blue")

dst2=ggplot(snow100_filter, aes(x = year1, y = snow)) + 
  geom_violin(aes(fill = year1), alpha = .5) + 
  stat_summary(fun = "median", color = "blue")
```

Let's draw a two-plant table
```{r}
tmx_tmin/dst1
tmx_tmin+dst2
```


